\documentclass{article}

\usepackage{geometry}
\geometry{left=3cm, right=3cm, bottom=3cm, top=3cm}
\usepackage[section]{placeins}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{dynkin-diagrams}
\usepackage{algorithm2e}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage[outline]{contour}
\contourlength{1.3pt}

% add shell-escape to commands
\usetikzlibrary{knots, cd, external, calc}
\tikzexternalize[prefix=tikz/]

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{examples}[theorem]{Examples}
\newtheorem{example}[theorem]{Example}
\newtheorem{notation}[theorem]{Notation}

\newcommand{\coxtwothreethree}{%
\begin{tikzpicture}[scale=0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\end{tikzpicture}}

\newcommand{\coxthreethreethree}{%
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) -- (60:1) -- (1, 0) -- (0, 0);
\draw[fill = white] (0, 0) circle (0.1);
\draw[fill = white] (60:1) circle (0.1);
\draw[fill = white] (1, 0) circle (0.1);
\end{tikzpicture}}

\newcommand{\coxthreethreethreetype}[1]{%
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) -- (60:1) -- (1, 0) -- (0, 0);
\draw[fill = white] (0, 0) circle (0.1);
\draw[fill = white] (60:1) circle (0.1);
\draw[fill = white] (1, 0) circle (0.1);
\node at (0.5, 0.2) {\tiny{#1}};
\end{tikzpicture}}

\newcommand{\coxathreetype}[1]{%
\begin{tikzpicture}[scale=0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);

\node at (0.5, 0.2) {\tiny{#1}};
\end{tikzpicture}}

\newcommand{\coxathreetypedouble}[2]{%
\begin{tikzpicture}[scale=0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);

\node at (0.5, 0.2) {\tiny{#1}};
\node at (1.5, 0.2) {\tiny{#2}};
\end{tikzpicture}}

\newcommand{\coxfourthreethree}{%
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) -- (60:1) -- (1, 0);
\draw (0, 0.05) -- (1, 0.05);
\draw (0, -0.05) -- (1, -0.05);
\draw[fill = white] (0, 0) circle (0.1);
\draw[fill = white] (60:1) circle (0.1);
\draw[fill = white] (1, 0) circle (0.1);
\end{tikzpicture}
}

\newcommand{\verticalcenter}[1]{
\begin{tabular}{l} #1 \end{tabular}
}

\begin{document}

\begin{titlepage}
\begin{center}
\pagenumbering{gobble}
\vspace*{1.5cm}
\Large{Department of Mathematics \\ of the University of Bern}\\
\vspace*{3.5cm}
\Huge{\textbf{Coxeter Quotients \\ of Link Groups}}\\
\vspace*{6.5cm}
\Large{Master Thesis of} \\ \Large{\textbf{Levi Ryffel}}\\
\vspace*{.25cm}
Supervised by \\ \textbf{Prof. Dr. Sebastian Baader}\\
\vspace*{2cm}
February 2020
\end{center}
\end{titlepage}
\pagenumbering{arabic}

\tableofcontents
\newpage

\section{Coxeter Groups}
Coxeter groups are of particular interest in geometric group theory, where they form a particularly nice family of examples \cite{davis2008}.
In this thesis we are going to exploit their nice properties and apply them to knot theoretic concepts such as the meridional rank, compare Section \ref{subsec:meridional-rank}.

In this section we are going to introduce the basics of the theory of Coxeter groups, limited to just what we will use afterwards. This is by no means a proper introduction; the reader completely unfamiliar with the theory of Coxeter groups might want to pick up \cite{humphreys1990} before reading what follows.

\subsection{Coxeter Matrices and Graphs}
Let $S$ be a finite set and let $M = (m_{st})$ be an $S \times S$ matrix with coefficients in the set of natural numbers, possibly $\infty$, satisfying $m_{ss} = 1$ for all $s \in S$, and $m_{st} \geq 2$ if $s \ne t$. Such a matrix is called a \textit{Coxeter matrix}. Consider the group presentation
$$W = \langle S \; | \; (st)^{m_{st}} = 1 \text{ for } s,t\in S \rangle,$$
where we do not include relations of the form $(st)^\infty = 1$.
Then the group $W$ is called the \textit{Coxeter group} corresponding to $M$. The tuple $(W,S)$ is called a \textit{Coxeter system} and the cardinality $\#S$ is referred to as its \textit{rank}. Since for us Coxeter groups always arise with a generating set, we blur the distinction between Coxeter groups and Coxeter systems.

Another way to encode the coefficients $m_{st}$ is to use them as weights in weighted undirected graphs, so-called \textit{Coxeter graphs}. In this case, the nodes of the graph associated to $W$ are the generators $S$, and the weight between the nodes $s$ and $t$ is $m_{st}$. The following shorthand notations are very common: If $m_{st} = 2$, then the edge between $s$ and $t$ is omitted and if $m_{st} = 3$, then the weight on the edge between $s$ and $t$ is omitted.

\begin{example}[Dihedral Groups]
The symmetry group of a regular $n$-gon is called the 
\textit{dihedral group} of order $2n$, denoted by the symbol $D_n$. This group is generated by two reflections 
$s, t$ whose composition is a rotation by an angle 
of~$2\pi/n$. This is used to show that $D_n$ 
is isomorphic to the Coxeter group
$$W = \langle s, t \; | \; (st)^n = s^2 = t^2 = 1 \rangle.$$
Thus, Coxeter groups on two generators whose product has finite order are dihedral groups.

This observation is often used to motivate the introduction of one more dihedral group, the so-called \textit{infinite dihedral group} with presentation
$$D_\infty = \langle s, t \; | \; s^2 = t^2 = 1 \rangle.$$
\end{example}
\subsection{The Reflection Representation}
A well-known construction leading to an easy solution of the word-problem for Coxeter groups and also helping in adapting a geometric viewpoint to the study of Coxeter groups is a faithful representation of any Coxeter group where its generating sets acts as a set of reflections with respect to a (possibly degenerate) bilinear form.

Let $(W,S)$ be a Coxeter system, and let $n = \#S$. Then we consider the bilinear form on $V = \mathbb{R}^S$ given by the matrix $B = (b_{st})$ with entries $b_{st} = -\cos \pi/m_{st}$. 
For $s \in S$ let $\rho_s$ be the \textit{reflection} with respect to $B$ with root $e_s \in \mathbb{R}^n$ given by the formula
$$ \rho_s(x) = x - 2B(x, e_s)e_s,$$
where $x \in V$.

\begin{proposition}\label{prop:reflection-representation-well-defined}
Let $(W,S)$ be a Coxeter system and let $s, t \in S$. Then the reflections $\rho_s$ and $\rho_t$ satisfy $(\rho_s \rho_t)^{m_{st}} = 1$.
\end{proposition}

\begin{proof}
First of all, observe that each reflection $\rho_s$ fixes an $(n-1)$-dimensional hyperplane, namely the orthogonal complement of the non-isotropic vector $e_s$. Now fix $s,t\in S$ and consider the subspace $V_{st} = \mathbb{R}e_s \oplus \mathbb{R}e_t$, which is invariant under $\rho_s$ and $\rho_t$. Since the orthogonal complement of $V_{st}$ is fixed by $\rho_s$ and $\rho_t$, the order of $\rho_s\rho_t$ on $V$ is equal to its order on $V_{st}$.

Let us now distinguish two cases. If $m_{st}$ is finite, $B$ restricted to $V_{st}$ is positive definite. To see this, consider an arbitrary vector $v = ae_s + b e_t$ in $V_{st}$ and compute
\begin{align*}
B(v, v) & = a^2B(e_s, e_s) + 2abB(e_s, e_t) + b^2B(e_t, e_t)\\
& = a^2 + 2ab\text{cos}( -\pi / m_{st} ) + b^2 \\
& > a^2 - 2ab + b^2 \\
& = (a - b)^2 \\
& \geq 0.
\end{align*}
Thus, $V_{st}$ is isometric to $\mathbb{R}^2$ with the standard inner product, and the angle between the invariant subspaces of $\rho_s$ and $\rho_t$ is equal to $2 \pi / m_{st}$. This shows that $\rho_s$ and $\rho_t$ are symmetries of a regular $n$-gon and their product is a rotation by $2\pi/m_{st}$, which has order $m_{st}$.

On the other hand, if $m_{st} = \infty$ the matrix of $\rho_s\rho_t$ is given by
$$\rho_s \rho_t = \left( \begin{matrix}
-1 & 1 \\ 1 & -1
\end{matrix} \right)
\left( \begin{matrix}
1 & -1 \\ -1 & 1
\end{matrix} \right)
= \left( \begin{matrix}
0 & 2 \\ 2 & 0
\end{matrix} \right)
$$
which has infinite order.
\end{proof}

This shows that the map $s \mapsto \rho_s$ induces a representation of $W$, called the \textit{reflection representation} of $W$. We will conclude this section by showing that this representation is faithful. But first we need some preparation.

To any Coxeter group $W$ we can assign a \textit{length function} $l: W \rightarrow \mathbb{N}$, assigning to any element $w$ of $W$ the minimal number of generating reflections needed to write down an expression for $w$. An expression for $w$ of length $l(w)$ is called a \textit{reduced expression} for $w$.

To get a little bit of a feeling how the length function behaves for Coxeter groups (or more generally, for groups generated by elements of order two subject only to relations of even length, such as the reflection quotient from Section \ref{subsec:reflection-quotient}), we prove the following illustrative result.

\begin{proposition}
Let $W$ be a Coxeter group, $w \in W$ and $s \in S$. Then either $l(ws) = l(w) + 1$ or $l(ws) = l(w) - 1$.
\end{proposition}

\begin{proof}
First of all, we make the obvious observation that for any words 
$w, w' \in W$ we have that $l(ww') \leq l(w) + l(w')$. This immediately implies that $l(ww') \geq l(w) - l(w')$ by applying the above to the pair $ww'$ and $w'^{-1}$ instead of $w$ and $w'$, observing that $l(w) = l(w^{-1})$ for all $w \in W$. We conclude that
$$l(w) - 1 \leq l(ws) \leq l(w) + 1.$$
The only thing left to show is that in fact $l(ws) \neq l(w)$. To see this, we introduce the \textit{sign} homomorphism $\varepsilon: W \rightarrow \{\pm 1\}$ defined via $s \mapsto -1$ for all $s \in S$. Indeed, this extends to $W$ since all relations of $W$ are of even length. Obviously we have $\varepsilon(w) = (-1)^{l(w)}$, and $\varepsilon(ws) \neq \varepsilon(w)$. This implies that $l(ws) \neq l(w)$, which is precisely what we wanted to show.
\end{proof}

For a vector $v$ in $V$ we will write $v > 0$ if $v$ is non-zero and is a non-negative linear combination of the $e_s$. Moreover, $v < 0$ if $-v>0$. This enables us to formulate the following important Lemma. A consequence of it that is easy to formulate and captures its essence goes as follows: Whenever $we_s$ lies in the positive cone, that is $w e_s > 0$, then $w$ does not have a reduced expression ending in $s$.

\begin{lemma}\label{lem:humphreys5.4}
Let $W$ be a Coxeter group, $w \in W$ and $s \in S$. Then $we_s > 0$ if and only if $l(ws) = l(w) + 1$.
\end{lemma}

\begin{proof}
This is taken from \cite{humphreys1990}. Note first that it suffices to prove that whenever $l(ws) = l(w) + 1$ we have that $we_s > 0$, since applying this to $ws$ instead of $w$ proves its converse. 

The proof of this direction is a proof by induction on $l(w)$. Suppose $l(w) = 0$. Then $w$ is the identity and $l(ws) = l(w) + 1$ for all $s$. 

For the inductive step, Let $t$ be any reflection in $S$ such that $l(wt) = l(w) - 1$, taking for example $t$ to be the last symbol in a reduced expression for $w$. Write $w = w'w_{st}$, where $w_{st}$ is a word in the symbols $s, t$ of maximal length such that the length of the expression $w'w_{st}$ is equal to $l(w)$. This exists since $w_{st}$ equal to the empty word is in fact a (non-maximal) solution.

We will now prove the Lemma by showing that $w'e_s > 0$, $w'e_t > 0$ and $w_{st}e_s > 0$, and that $w_{st}$ is non-empty. Taking $w_{st} = t$ shows that $l(w') < l(w)$, so we can apply the induction hypothesis to $w'$, showing that $w'e_s > 0$ and $w'e_t > 0$ provided we can show that $l(w's) > l(w')$ and $l(w't) > l(w')$. 

Suppose toward a contradiction that $l(w's) < l(w')$. Then $sw_{st}$ is in fact a longer word than $w_{st}$, contradicting maximality of $w_{st}$. Similarly it is also true that $l(w't) > l(w')$.


\begin{figure}[ht]
\centering
\begin{minipage}{.5\textwidth}
\centering
\begin{tikzpicture}[scale = 0.5]
% pentagon
\filldraw[color = black!20] (4, 0) -- (72:4) -- (144:4) -- (0, 0);
\draw[thick] (4, 0) -- (72:4) -- (144:4) -- (216:4) -- (288:4) -- (4, 0);
\draw[thick, dashed] (-5, 0) -- (5, 0);
\draw[thick, dashed] (144:5) -- (144:-5);
\draw (0, -5) -- (0, 5);
\draw (54:5) -- (54:-5);

\node at (4, 0) {\contour{white}{$e_s$}};
\node at (144:4) {\contour{white}{$e_t$}};
\node at (0, 4) {\contour{white}{$e_s^\perp$}};
\node at (54:4) {\contour{white}{$e_t^\perp$}};


\end{tikzpicture}
\end{minipage}%
\begin{minipage}{.5\textwidth}
\centering

\begin{tikzpicture}[scale = 0.5]
% hexagon
\filldraw[color = black!20] (4, 0) -- (60:4) -- (120:4) -- ($(120:4)!0.5!(180:4)$) -- (0, 0);
\draw[thick] (4, 0) -- (60:4) -- (120:4) -- (180:4) -- (60:-4) -- (120:-4) -- (4, 0);

\draw[thick, dashed] (-5, 0) -- (5, 0);
\draw[thick, dashed] (150:5) -- (150:-5);
\draw (0, -5) -- (0, 5);
\draw (60:5) -- (60:-5);

\node at (4, 0) {\contour{white}{$e_s$}};
\node at (150:4) {\contour{white}{$e_t$}};
\node at (60:4) {\contour{white}{$e_t^{\perp}$}};
\node at (90:4) {\contour{white}{$e_s^\perp$}};

\end{tikzpicture}
\end{minipage}
\caption{Illustration of the fact that $e_s$ lands in the positive cone, indicated in grey. Note that composing reflections in the mirrors $e_s^\perp$ and $e_t^\perp$ results in a rotation by an angle of $2\pi/m_{st}$.}
\end{figure}

Finally we draw a picture to show that $v_{st}e_s > 0$. Note first that $v_{st}$ does not have a reduced expression ending in $s$, since if it did we would actually reduce its length by adding an $s$ to the end. In particular, the length of $w_{st}$ is strictly less than $m_{st}$, that is, interpreting $w_{st}$ as a map on the plane as in the proof of Proposition \ref{prop:reflection-representation-well-defined}, $w_{st}$ is not rotation by an angle of $\pi$. The claim now follows from the fact that $w_{st}$ is a rotation by at most $\pi - \pi/m$, perhaps followed by a reflection in $e_t^\perp$, but only if this does not result in a rotation by an angle of~$\pi$.
\end{proof}

Having established how the length function is related to the action of $W$ on the basis vectors of its geometric representation, we immediately obtain what we desired.

\begin{theorem}
The reflection representation is faithful.
\end{theorem}

\begin{proof}
Suppose $w$ lies in the kernel of the reflection representation. Then obviously $we_s > 0$ for all $s \in S$, so by Lemma \ref{lem:humphreys5.4}, $l(ws) = l(w) + 1$ for all $s \in S$, i.e., for any $s \in S$ we have that $w$ does not have a reduced expression ending in $s$. But this implies that $w$ is the identity.
\end{proof}

\subsection{Roots}\label{subsec:roots}
The main goal of this section is to show that Coxeter groups have tiny center, that is, the center of an infinite Coxeter group is trivial. To do this, our main tool will be the action of a Coxeter group on a specific subset of $V$ called roots.

The set of \textit{roots} of a Coxeter group $W$, denoted by the letter $\Phi$, is the set of all images of the basis vectors $e_s$ under $W$. The geometric observation justifying this terminology is the following. Let $w$ be an arbitrary element of $W$. Then, for all generating reflections $s \in S$, the map $wsw^{-1}$ acts on $V$ by a reflection whose eigenvector of eigenvalue one is the vector $we_s$.

Note that by Lemma \ref{lem:humphreys5.4}, every root is either positive or negative. Writing $\Pi$ for the set of positive roots, we can express this in symbols as $\Phi = \Pi \cup -\Pi$. This will be useful for a geometric characterization of the length function $l$ on a Coxeter group. Consider the function $n$ mapping an element $w \in W$ to the number of positive roots sent to negative roots by the action of $w$ on $V$.

\begin{proposition}\label{prop:n=l}
Let $W$ be a Coxeter group. Then, for any element $w$ of $W$ we have that $n(w) = l(w)$.
\end{proposition}

\begin{proof}
Let $s \in S$. We first prove that the only positive root mapped to a negative root by $s$ is the basis vector $e_s$. Choose any positive root $\alpha \neq e_s$. Since $\alpha$ is not equal to $e_s$ there exists a reflection $t \in S$ such that the coefficient of $\alpha$ corresponding to the $e_t$-component of $\alpha$ is non-zero. But the reflection $s$ does not change the $e_t$-component of $\alpha$, so $s\alpha$ must be positive.

We now proceed by induction on $l(w)$. Suppose $l(ws) > l(w)$, and that $n(w) = l(w)$. By Lemma \ref{lem:humphreys5.4} it follows that $we_s > 0$, which immediately implies that $wse_s = -we_s < 0$. Note that since $w$ induces a bijection on the remaining positive roots $\Pi \setminus \{e_s\}$, we must have $n(ws) = n(w) + 1 = l(ws)$.
\end{proof}

Recall that the \textit{radical} $V^\perp$ of the bilinear form $B$ on $V$ is the set of vectors~$v'$ in $V$ such that $B(v, v') = 0$ for all $v$ in $V$. Note that $V^\perp$ is not affected by any reflection, so in particular $V^\perp$ is a $W$-invariant subspace. We will now prove a partial converse to this for \textit{irreducible} Coxeter groups, that is, Coxeter groups whose associated Coxeter graph is connected.

\begin{theorem}\label{thm:invariant-subspaces}
Let $W$ be an irreducible Coxeter group. Then, every proper $W$-invariant subspace of $V$ is contained in $V^\perp$.
\end{theorem}

\begin{proof}
Let $V'$ be a $W$-invariant subspace of $V$. Suppose first that some basis vector $e_s$ is contained in $V'$. Let $t$ be adjacent to $s$ in the Coxeter graph of $W$. Then $te_s$ has a non-zero $e_t$-component and is contained in $V'$, so it follows that also $e_t$ is in $V'$. Proceeding like this through the connected Coxeter graph of $W$ we obtain that $V'$ contains a basis of $V$. Therefore, $V'$ is not a proper subspace.

We have established that all proper $W$-invariant subspaces of $V$ do not contain any basis vectors $e_s$. Let $V'$ be such a subspace. Then $V'$ is contained in an intersection of eigenspaces of the generating reflections $s \in S$. But since the proper subspace $V'$ does not contain the basis vectors $e_s$, we have that $V'$ must be contained in the eigenspaces of $s \in S$ of eigenvalue $1$, in other words, in the orthogonal complements of the basis vectors $e_s$.
\end{proof}

\begin{corollary}
The center of an infinite Coxeter group is trivial.
\end{corollary}

\begin{proof}
Let $A$ be any endomorphism of $V$ commuting with every element of $W$. We will show that $A$ is actually multiplication with a scalar. Let $s \in S$ be any generating reflection. Since $A$ commutes with $s$ their eigenspaces must agree. In particular, the line $\mathbb{R}e_s$ is an eigenspace of $A$ of eigenvalue $c$ for some $c$. 

Let $V'$ be the kernel of the map $A-c$. Let $v \in V'$. Then $Av = cv$. But then we have
\begin{align*}
(A-c)wv & = Awv - cwv \\
& = wAv - cwv \\
& = w(A - c) v \\
& = 0,
\end{align*}
so $V'$ is $W$-invariant. Since $V'$ contains $\mathbb{R}e_s$ and since $\mathbb{R}e_s$ is not contained in $V^\perp$, we obtain by Theorem \ref{thm:invariant-subspaces} that $V' = V$, in other words, that $A$ is multiplication with $c$.

We now consider what happens if $A$ is actually an element of $W$. If $c > 0$ then all roots in $\Pi$ are mapped to positive roots, so by Lemma \ref{lem:humphreys5.4} we have that $A$ is the identity. If $c < 0$ we first make the following observation: $\Pi$ is finite if and only if $W$ is. Now observe that all positive roots in $\Pi$ are mapped to negative roots, so the length of $A$ as an element of $W$ is infinite by Lemma \ref{lem:humphreys5.4}, which is absurd.
\end{proof}

\subsection{Conjugacy Classes}\label{subsec:conjugacy-classes}
Imposing as the title of this section may sound, we are not going to be able to give a description of how conjugacy classes work in Coxeter groups. We will however be able to determine the number of conjugacy classes in the set of reflections.

Let $W$ be a Coxeter group generated by the set $S$. A \textit{reflection} is an element $w \in W$ that is conjugate to an element in $S$. We will write $T$ for the set of reflections.

\begin{proposition}\label{prop:conjugacy}
Let $\Gamma$ be the Coxeter graph of a Coxeter group $W$, and let $s, t \in S$. Then $s$ and $t$ are conjugate if and only if there exists a path in $\Gamma$ from $s$ to $t$ whose edges only consist of odd weights.
\end{proposition}

\begin{proof}
Recall that being conjugate is an equivalence relation. By transitivity it suffices to prove, for sufficiency, that if there exists a relation $(st)^{m_{st}}$ for odd $m_st$, that $s$ and $t$ are conjugate. But with this relation we have for $k = (m-1)/2$ that $t = (st)^ks(ts)^k$.

We prove the converse by contraposition. If there exists no such path between $s$ and $t$, the subgraph $\Gamma_0$ of $\Gamma$ consisting of the same vertices but only of the odd weighted edges is disconnected. Moreover, $s$ and $t$ lie in distinct path-components of $\Gamma_0$. Let $\varepsilon: W \rightarrow \{\pm1\}$ be the homomorphism induced by sending each reflection in $S$ that lies in the same component as $s$ to $-1$, and each of the other reflections to $1$. This is well-defined. To see this, note that two elements in $S$ that are not sent to the same element of $\{\pm1\}$ only have odd weights between them, so the defining relators in $W$ indeed lie in the kernel of $\varepsilon$ considered as a map on the free group $F(S)$.

Thus, $\varepsilon$ is a homomorphism to an abelian group mapping $s$ and $t$ to distinct elements. But since the image of a conjugacy class lies in one conjugacy class, this shows that $s$ and $t$ are not conjugate.
\end{proof}

Let $\Gamma_0$ be as in the proof of Proposition \ref{prop:conjugacy}. Then we can restate the above as follows: \textit{There is exactly one conjugacy class in $T$ for each component of $\Gamma_0$}. In particular, all reflections in $W$ are conjugate if and only if $\Gamma_0$ is connected.

\subsection{The Word Problem}
\begin{notation}
Let $W$ be a Coxeter group with generating set $S$ and Coxeter matrix $M = (m_{st})$. Then we agree on the convention that
$$(st)^{m_{st}/2} =  \begin{cases}
(st)^k & \text{ if } m_{st} = 2k, \\
(st)^ls & \text{ if } m_{st} = 2l + 1.
\end{cases}$$
E.g., if $m_{st}=5$ we write $(st)^{5/2} = ststs$. 
\end{notation}

%TODO cite properly
\begin{theorem}[Tits]\label{thm:word-problem}
Let $F$ be the free monoid generated by the set $S$. Suppose the word $w \in F$ represents the trivial element in a Coxeter group $W$ with generating set $S$ and Coxeter matrix $M = (m_{st})$. Then there is a sequence of moves of the following two types carrying $w$ to the empty word.

\begin{enumerate}[\textup{(}i\textup{)}]
\setlength\itemsep{0em}
\item removing occurrences of $s^2$ from $w$ for $s \in S$.
\item replacing occurrences of $(st)^{m_{st}/2}$ by $(ts)^{m_{st}/2}$ for $s, t \in S$.
\end{enumerate}
In particular, there is a sequence of the above moves carrying $w$ to the empty word without making $w$ longer.
\end{theorem}

\subsection{Finite Coxeter Groups}
Finite Coxeter groups differ from infinite ones in a few key ways. For example, with the techniques introduced in Section \ref{subsec:roots} we can prove the following interesting result.

\begin{theorem}
Let $W$ be a finite Coxeter group. Then $W$ has a unique longest element $w_0$.
\end{theorem}

\begin{proof}
Note that by Proposition \ref{prop:n=l} we have that the length function is bounded from above by the cardinality $|\Pi|$. Moreover, if $w \in W$ sends all $e_s$ to negative roots, then $we_s$ is a negative linear combination of basis vectors, whence $w$ sends all positive roots to negative roots. In other words, if $w \in W$ is not of length $|\Pi|$, then there exists a basis vector $e_s$ not sent to a negative root. But then, by Lemma \ref{lem:humphreys5.4} the word $ws$ is longer than $w$. This shows that the length $|\Pi|$ is actually attained by some word $w_0 \in W$.

If $w_1$ is another word of maximal length, we have that $w_0w_1$ maps all positive roots to positive roots, so by Proposition \ref{prop:n=l} we have that its length is zero, i.e., $w_0w_1$ is the identity. It follows that $w_0 = w_1$.
\end{proof}

It turns out that finite Coxeter groups can be completely classified. This feat was first accomplished in \cite{coxeter1935}. The classification of finite irreducible Coxeter groups will be useful for us in Section \ref{sec:torus-knots}. Since this is a well-documented exercise in combinatorial graph theory, see \cite{humphreys1990}, we will omit the proof and only state the theorem.

\begin{theorem}
Any finite irreducible Coxeter group can be found in Table \ref{tab:classification}.
\end{theorem}
%TODO cite
\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Coxeter Graph & Name & Size \\
\hline
\begin{tabular}{l}\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\node at (2.75, 0) {$\cdots$};
\draw (3.5, 0) circle (0.1);
\draw (4.5, 0) circle (0.1);
\draw (5.5, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (3.6, 0) -- (4.4, 0);
\draw (4.6, 0) -- (5.4, 0);
\end{tikzpicture}
\end{tabular} & \begin{tabular}{l} $A_n$ \end{tabular} & \begin{tabular}{l}$(n+1)!$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\node at (2.75, 0) {$\cdots$};
\draw (3.5, 0) circle (0.1);
\draw (4.5, 0) circle (0.1);
\draw (5.5, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (3.6, 0) -- (4.4, 0);
\draw (4.6, 0) -- (5.4, 0);
\node at (0.5, 0.2) {\tiny{$4$}};
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$B_n$\end{tabular} & \begin{tabular}{l}$2^n n!$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\node at (2.75, 0) {$\cdots$};
\draw (3.5, 0) circle (0.1);
\draw (4.5, 0) circle (0.1);
\draw ($(4.5, 0) + (30:1)$) circle (0.1);
\draw ($(4.5, 0) + (-30:1)$) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (3.6, 0) -- (4.4, 0);
\draw ($(4.5, 0) + (30:0.1)$) -- ($(4.5, 0) + (30:0.9)$);
\draw ($(4.5, 0) + (-30:0.1)$) -- ($(4.5, 0) + (-30:0.9)$);
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$D_n$\end{tabular} & \begin{tabular}{l}$2^{n-1} n!$\end{tabular} \\
\begin{tabular}{l}\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (3, 0) circle (0.1);
\draw (4, 0) circle (0.1);
\draw (2, 1) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (2.1, 0) -- (2.9, 0);
\draw (3.1, 0) -- (3.9, 0);
\draw (2, 0.1) -- (2, 0.9);
\end{tikzpicture}\end{tabular}& \begin{tabular}{l}$E_6$\end{tabular} & \begin{tabular}{l}$72 \cdot 6!$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (3, 0) circle (0.1);
\draw (4, 0) circle (0.1);
\draw (5, 0) circle (0.1);
\draw (2, 1) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (2.1, 0) -- (2.9, 0);
\draw (3.1, 0) -- (3.9, 0);
\draw (2, 0.1) -- (2, 0.9);
\draw (4.1, 0) -- (4.9, 0);
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$E_7$\end{tabular} & \begin{tabular}{l}$72 \cdot 8!$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (3, 0) circle (0.1);
\draw (4, 0) circle (0.1);
\draw (5, 0) circle (0.1);
\draw (6, 0) circle (0.1);
\draw (2, 1) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (2.1, 0) -- (2.9, 0);
\draw (3.1, 0) -- (3.9, 0);
\draw (2, 0.1) -- (2, 0.9);
\draw (4.1, 0) -- (4.9, 0);
\draw (5.1, 0) -- (5.9, 0);
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$E_8$\end{tabular} & \begin{tabular}{l}$192 \cdot 10!$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (3, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (2.1, 0) -- (2.9, 0);
\node at (1.5, 0.2) {\tiny{$4$}};
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$F_4$\end{tabular} & \begin{tabular}{l}$1152$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\node at (0.5, 0.2) {\tiny{$5$}};
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$H_3$\end{tabular} & \begin{tabular}{l}$120$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (2, 0) circle (0.1);
\draw (3, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\draw (1.1, 0) -- (1.9, 0);
\draw (2.1, 0) -- (2.9, 0);
\node at (0.5, 0.2) {\tiny{$5$}};
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$H_4$\end{tabular} & \begin{tabular}{l}$14400$\end{tabular} \\
\begin{tabular}{l}
\begin{tikzpicture}[scale = 0.5]
\draw (0, 0) circle (0.1);
\draw (1, 0) circle (0.1);
\draw (0.1, 0) -- (0.9, 0);
\node at (0.5, 0.2) {\tiny{$n$}};
\end{tikzpicture}
\end{tabular}& \begin{tabular}{l}$I_2(n)$\end{tabular} & \begin{tabular}{l}$2n$\end{tabular}
\end{tabular}
\caption{Classification of Irreducible Finite Coxeter Groups}
\label{tab:classification}
\end{table}

\newpage

\section{Knot Theory}
\subsection{Knots and Links}
A \textit{knot} $K$ is the image of a smooth embedding of $S^1$ into $S^3$. A \textit{link} $L$ is a disjoint union of finitely many knots. Two links $L \subset S^3$ and $L' \subset S^3$ are said to be \textit{equivalent} if there exists a diffeomorphism between the pair $(S^3, L)$ and the pair $(S^3, L')$, i.e., a diffeomorphism $S^3 \rightarrow S^3$ that restricts to a diffeomorphism of the links $L \rightarrow L'$.



\begin{example}[Torus Links]
Let $p, q$ be integers. Consider the universal covering $\mathbb{R}^2 \rightarrow T^2$, where $T^2 \subset \mathbb{R}^3$ is a standardly embedded torus (consider e.g. Example 6 of Section 2-2 in \cite{docarmo1976}). Then the $(p,q)$-\textit{torus link} is the image of the lines through $\mathbb{Z}e_1$ of slope $p/q$. Actually no but almost.
\end{example}

\begin{example}[Pretzel Links]
The $(l_1, \dots, l_k)$-\textit{Pretzel link} is the link obtained by connecting 2-braids in the way indicated in Figure \ref{fig:pretzel-link}.
%TODO introduce 2-braids

\begin{figure}[ht]
\centering
\begin{minipage}{0.5\textwidth}
\centering
\begin{tikzpicture}[scale = 0.8]
\draw[ultra thick] (0, 0) rectangle (1,4);
\draw[ultra thick] (2, 0) rectangle (3, 4);
\node at (3.6, 2) [circle, fill, inner sep=1pt] {};
\node at (4,2) [circle, fill, inner sep=1pt] {};
\node at (4.4, 2) [circle, fill, inner sep=1pt] {};
\draw[ultra thick] (5, 0) rectangle (6, 4);

\begin{knot}
\strand[thick] (0.25, 4) .. controls +(0, 1) and +(0, 1) .. (5.75, 4);
\strand[thick] (0.75, 4) .. controls +(0, 0.2) and +(0, 0.2) .. (2.25, 4);
\strand[thick] (2.75, 4) .. controls +(0, 0.2) and +(0, 0.2) .. (5.25, 4);

\strand[thick] (0.25, 0) .. controls +(0, -1) and +(0, -1) .. (5.75, 0);
\strand[thick] (0.75, 0) .. controls +(0, -0.2) and +(0, -0.2) .. (2.25, 0);
\strand[thick] (2.75, 0) .. controls +(0, -0.2) and +(0, -0.2) .. (5.25, 0);
\end{knot}

\node at (0.5, 2) {$l_1$};
\node at (2.5, 2) {$l_2$};
\node at (5.5, 2) {$l_k$};

\end{tikzpicture}
\caption{$P(l_1, l_2, \dots, l_k)$}
\label{fig:pretzel-link}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\centering
\begin{tikzpicture}[scale = 0.8]

\draw[ultra thick] (0, -0.5) rectangle (1, 3.5);
\draw[ultra thick] (2, -0.5) rectangle (3, 3.5);
\draw[ultra thick] (4, -0.5) rectangle (5, 3.5);

\begin{knot}[clip width = 5, flip crossing/.list={2, 4, 6, 8}]
\strand[thick] (0.25, -0.5) -- (0.25, 0.5) .. controls +(0, 0.5) and +(0, -0.5) .. (0.75, 1.5) .. controls +(0, 0.5) and +(0, -0.5) .. (0.25, 2.5) -- (0.25, 3.5);

\strand[thick] (0.75, -0.5) -- (0.75, 0.5) .. controls +(0, 0.5) and +(0, -0.5) .. (0.25, 1.5) .. controls +(0, 0.5) and +(0, -0.5) .. (0.75, 2.5) -- (0.75, 3.5);


\strand[thick] (2.25, -0.5) -- (2.25, 0) .. controls +(0, 0.5) and +(0, -0.5) .. (2.75, 1) .. controls +(0, 0.5) and +(0, -0.5) .. (2.25, 2) .. controls +(0, 0.5) and +(0, -0.5) .. (2.75, 3) -- (2.75, 3.5);

\strand[thick] (2.75, -0.5) -- (2.75, 0) .. controls +(0, 0.5) and +(0, -0.5) .. (2.25, 1) .. controls +(0, 0.5) and +(0, -0.5) .. (2.75, 2) .. controls +(0, 0.5) and +(0, -0.5) .. (2.25, 3) -- (2.25, 3.5);



\strand[thick] (4.25, -0.5) -- (4.25, 0) .. controls +(0, 0.5) and +(0, -0.5) .. (4.75, 1) .. controls +(0, 0.5) and +(0, -0.5) .. (4.25, 2) .. controls +(0, 0.5) and +(0, -0.5) .. (4.75, 3) -- (4.75, 3.5);

\strand[thick] (4.75, -0.5) -- (4.75, 0) .. controls +(0, 0.5) and +(0, -0.5) .. (4.25, 1) .. controls +(0, 0.5) and +(0, -0.5) .. (4.75, 2) .. controls +(0, 0.5) and +(0, -0.5) .. (4.25, 3) -- (4.25, 3.5);

\strand[thick] (0.75, -0.5) .. controls +(0, -0.2) and +(0, -0.2) .. (2.25, -0.5);
\strand[thick] (2.75, -0.5) .. controls +(0, -0.2) and +(0, -0.2) .. (4.25, -0.5);
\strand[thick] (0.25, -0.5) .. controls +(0, -1) and +(0, -1) .. (4.75, -0.5);


\strand[thick] (0.75, 3.5) .. controls +(0, 0.2) and +(0, 0.2) .. (2.25, 3.5);
\strand[thick] (2.75, 3.5) .. controls +(0, 0.2) and +(0, 0.2) .. (4.25, 3.5);
\strand[thick] (0.25, 3.5) .. controls +(0, 1) and +(0, 1) .. (4.75, 3.5);


\end{knot}
\end{tikzpicture}
\caption{$P(2, 3, -3)$}
\end{minipage}
\end{figure}
\end{example}
\subsection{The Bridge Index}
Let $L \subset S^3$ be a link. The minimal number of local maxima of a smooth function $S^3 \rightarrow \mathbb{R}$ restricted to $L$ is called the \textit{bridge index} of $L$ and referred to as $\text{bi } L$.

This can be diagrammatically characterized in the following way. Let $D$ be a diagram of $L$. An \textit{arc} in $D$ is a segment of $D$ beginning and ending with an undercrossing, containing no undercrossings in between. A \textit{bridge} of $D$ is an arc of $D$ that contains at least one overcrossing.

\begin{proposition}
The bridge index of a link $L \subset S^3$ is equal to the number of bridges in a diagram $D$ of $L$, minimized over all diagrams.
\end{proposition}

%TODO prove or cite


The following was first proven in \cite{schubert1954}.

\begin{proposition}\label{prop:bridge-index-connected-sum}
Let $K$ and $K'$ be knots. Then $\textup{bi } K\#K' = \textup{bi } K + \textup{bi }K' - 1$.
\end{proposition}


\subsection{The Link Group}\label{subsec:link-group}
The \textit{link group} of a link $L \subset S^3$ is $\pi(L) = \pi_1(S^3 \setminus L)$. If $L$ is a knot $K$ then the link group $\pi(K)$ is referred to as its \textit{knot group}.

The knot group essentially classifies all knots, in that if two knots have isomorphic knot groups then they are equivalent \cite{gordon1989}. Be warned that this is no longer true for links, see \cite{rolfsen2003}. This suggests that studying the knot group might be just as good as studying knots themselves.

We will now describe an algorithm that computes the link group of an oriented link. Let $L \subset S^3$ be a link and let $D$ be any diagram of $L$. Let $S = \{m_1, \dots, m_k\}$ be the set of diagram meridians, oriented from right to left. A meridian $m_i$ should be interpreted at as the meridian starting at the reader's eye, passing under the arc and going back to the reader's eye without any detour.

Having assigned a generator to every crossing, we now assign a relator $r$ to any crossing, as indicated in Figure \ref{fig:wirtinger-relations}.

\begin{figure}[ht]
\centering
\begin{minipage}{.5\textwidth}
\centering
\begin{tikzpicture}
\begin{knot}[clip width = 5]
\strand[black, thick, ->] (0, 0) -- (4, 4);
\strand[black, thick, ->] (4, 0) -- (0, 4);

\strand[black, ->] (1.9, 1.1) -- (1.1, 1.9);
\strand[black, ->] (1.9, 2.9) -- (1.1, 2.1);
\strand[black, ->] (2.9, 2.1) -- (2.1, 2.9);
\strand[black, ->] (2.9, 1.9) -- (2.1, 1.1);

\node at (1, 1.5) {$a$};
\node at (1, 2.5) {$b$};
\node at (2.5, 3) {$a$};
\node at (2.5, 1) {$c$};

\node at (2, 0) {$ca = ab$};
\end{knot}
\end{tikzpicture}
\end{minipage}%
\begin{minipage}{.5\textwidth}
\centering
\begin{tikzpicture}
\begin{knot}[clip width = 5]
\strand[black, thick, ->] (0, 0) -- (4, 4);
\strand[black, thick, ->] (0, 4) -- (4, 0);

\strand[black, ->] (1.9, 1.1) -- (1.1, 1.9);
\strand[black, ->] (1.1, 2.1) -- (1.9, 2.9);
\strand[black, ->] (2.9, 2.1) -- (2.1, 2.9);
\strand[black, ->] (2.1, 1.1) -- (2.9, 1.9);

\node at (1, 1.5) {$a$};
\node at (1.5, 3) {$c$};
\node at (2.5, 3) {$a$};
\node at (3, 1.5) {$b$};

\node at (2, 0) {$ba = ac$};
\end{knot}
\end{tikzpicture}
\end{minipage}
\caption{Relations in the Wirtinger Presentation}
\label{fig:wirtinger-relations}
\end{figure}

The fact that the resulting presentation is actually a presentation for the link group of $L$ is a Seifert-van Kampen argument, elaborated upon for example in \cite{rolfsen2003}.
%TODO do this

\subsection{Ribbons}
A \textit{ribbon disk} is a smooth immersion $D \rightarrow S^3$ of a disk $D$ that only has single and double points such that it becomes an embedding after removing finitely many intervals from the interior of $D$. A \textit{ribbon knot} is a knot that bounds a ribbon disk.

This can be visualized as follows. Let us call connected components of double points of a ribbon disk \textit{ribbon singularities}. Then a ribbon singularity looks like a slit cut into the interior of the ribbon in order to allow another part of the ribbon to pass through, see Figure \ref{fig:ribbon-singularity}. The singularity in Figure \ref{fig:not-ribbon-singularity} is not a ribbon singularity because the slit that we would need to cut involves a part of the boundary of the ribbon.

\begin{figure}[htb]
\centering
\begin{minipage}{0.5\textwidth}
\centering
\begin{tikzpicture}
\clip (0, -2) rectangle (6, 4);
\shade[left color=black!20, right color = black!10] (0, 0) rectangle (6, 2);
\shade[top color=black!40, bottom color = black!20] (2, -2) -- (2, 4) -- (4, 4) -- (4, 2) -- (3, 2) -- (3, 0) -- (4, 0) -- (4, -2) -- (2, -2);
\draw[thick] (1.9, 0) -- (0, 0);
\draw[thick] (0, 2) -- (1.9, 2);
\draw[thick] (3, 2) -- (6, 2);
\draw[thick] (6, 0) -- (3, 0);
\draw[thick, dashed] (3, 0) -- (3, 2);
\draw[thick] (4, 2.1) -- (4, 4);
\draw[thick] (2, 4) -- (2, -2);
\draw[thick] (4, -2) -- (4, -0.1);
\end{tikzpicture}
\caption{A ribbon singularity}
\label{fig:ribbon-singularity}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\centering
\begin{tikzpicture}
\clip (0, -2) rectangle (6, 4);
\shade[left color=black!20, right color = black!10] (0, 0) rectangle (6, 2);
\shade[top color=black!40, bottom color = black!20] (2, -2) -- (2, 0) .. controls +(0, 1) and +(-1, 0) .. (3, 1) -- (3, 0) -- (4, 0) -- (4, -2) -- (2, -2);

\draw[thick] (1.9, 0) -- (0, 0);
\draw[thick] (0, 2) -- (6, 2);
\draw[thick] (3, 0) -- (6, 0);
\draw[thick, dashed] (3, 0) -- (3, 1);
\draw[thick] (2, -2) -- (2, 0) .. controls +(0, 1) and +(-1, 0) .. (3, 1);
\draw[thick] (4, -2) -- (4, -0.1);
\end{tikzpicture}
\caption{Not a ribbon singularity}
\label{fig:not-ribbon-singularity}
\end{minipage}
\end{figure}

We start by considering a particular family of diagrams yielding ribbon knots.

\begin{theorem}
Let $K$ be any knot and $\bar{K}$ its mirror image. Then the connected sum $K\#\bar{K}$ is a ribbon knot.
\end{theorem}

\begin{proof}%[Proof sketch]
Suppose $P$ is the plane such that orthogonal reflection in $P$ throws the knot $K\#\bar{K}$ onto itself. In Figure \ref{fig:connected-sum-figure-8} the plane $P$ is represented by the dashed line. Now connect corresponding points on the knot by straight lines perpendicular to $P$. 
\end{proof}

\begin{figure}[htb]
%TODO flip crossings and fix shitty look
\centering
\begin{tikzpicture}[scale=0.8]
\clip (-4, -2) rectangle (4, 5);
\begin{knot}[clip width = 5, consider self intersections = true, 
ignore endpoint intersections=false,
%draft mode = crossings,
%flip crossing/.list = {10, 13, 2, 5}
]
\strand[thick] (0, 0) -- (2, 0) .. controls +(1, 0) and +(0, -1)
					  .. (1.5, 4) .. controls +(0, 0.5) and +(0, 0.5)
					  .. (2.5, 4) .. controls +(0, -1) and +(0, 1)
					  .. (1.5, 2) .. controls +(0, -1) and +(-1, 0)
					  .. (3, -1) .. controls +(1, 0) and +(1, 0)
					  .. (2.5, 4) -- (0, 4) 
					  -- (-2.5, 4) .. controls +(-1, 0) and +(-1, 0)
					  .. (-3, -1) .. controls +(1, 0) and +(0, -1)
					  .. (-1.5, 2) .. controls +(0, 1) and +(0, -1)
					  .. (-2.5, 4) .. controls +(0, 0.5) and +(0, 0.5)
					  .. (-1.5, 4) .. controls +(0, -1) and +(-1, 0)
					  .. (-2, 0) -- (0, 0);
\end{knot}
\draw[thick, dashed] (0, -1) -- (0, 4.5);
\end{tikzpicture}
\caption{The connected sum of the Figure-8 with its mirror image}
\label{fig:connected-sum-figure-8}
\end{figure}
\newpage

\section{Coxeter Quotients}
\subsection{The Reflection Quotient}\label{subsec:reflection-quotient}
Let $L \subset S^3$ be a link. A \textit{Coxeter quotient} is a quotient $\pi(K)/N$ of the link group which is isomorphic to a Coxeter group $W(M)$ such that every meridian in $\pi(L)$ corresponds to a reflection in $W(M)$.

In many cases, finding Coxeter quotients of links is rather straight-forward, at least with the help of a computer. This is because checking whether a specific set of Coxeter relations induces a Coxeter quotient of a link amounts to checking the validity of the defining relations in its link group.

The \textit{reflection quotient} is the group $r(L) = \pi_1(S^3 \setminus L) / \langle \langle m^2 \rangle \rangle$, where $m$ is any meridian of $L$. Because it is clumsy to write down a presentation in this fashion we agree to add the relations $s^2$ for all $s \in S$ when writing a presentation as $\langle S \; | \; R \rangle^{(2)}$. In this notation, the reflection quotient can be defined to be
$$r(L) = \pi(L)^{(2)}.$$

Coxeter quotients of a link $L$ are also quotients of $r(L)$. The fact justifying the study of quotients of $r(K)$ lies in the following theorem.

\begin{theorem}[Boileau-Zimmermann \cite{boileau1989}, Theorem 1]
Let $K$ and $K'$ be knots such that $r(K)$ and $r(K')$ are infinite. Then $K$ and $K'$ are equivalent if and only if $r(K)$ and $r(K')$ are isomorphic.
\end{theorem}

Be warned that in \cite{boileau1989} the reflection quotient is denoted $O(L)$ and is called the $\pi$-orbifold group.

It is easy to write down a presentation of the reflection quotient from a presentation of the link group $\pi(L) = \langle S \; | \; R \rangle$ of a link $L \subset S^3$. Just add the relations $s^2$ for all $s \in S$, and simplify $R$ by replacing all occurrences of $s^{-1}$ by $s$ and all occurrences of $s^2$ by the empty word. These presentations are generally shorter, easier to read and less prone to mistakes since it is no longer possible to confuse meridians with their inverses.

Note in addition that the Wirtinger algorithm (see Section \ref{subsec:link-group}) can be simplified so that the relation $ca = ab$ in Figure \ref{fig:wirtinger-relations} reads $acab = 1$ in the reflection quotient.
For these reasons, we will now mainly consider the reflection quotient instead of the link group.


\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{knot}[consider self intersections = true, clip width = 5, ignore endpoint intersections=false,
%draft mode = crossings,
flip crossing/.list={3, 5, 7}]
\strand[thick] (-0.5, 0) .. controls +(0, 1) and +(0, 1) .. (3, 1) .. controls +(0, -1) and +(1.5, 0) .. (0, -2) .. controls +(-1.5, 0) and +(0, -1) .. (-3, 1) .. controls +(0, 1) and +(0, 1) .. (0.5, 0) .. controls +(0, -1) and +(0, -1) .. (-3, -1) .. controls +(0, 1) and +(-1.5, 0) .. (0, 2) .. controls +(1.5, 0) and +(0, 1) .. (3, -1) .. controls +(0, -1) and +(0, -1) .. (-0.5, 0);
\end{knot}

\node at (3.3, 1) {$a$};
\node at (3.3, -1) {$b$};
\node at (-3.3, -1) {$c$};
\end{tikzpicture}
\caption{The knot $8_5$}
\label{fig:8-5}
\end{figure}

\begin{example}[The Knot $8_5$]
Consider $K = 8_5$ from Rolfsen's knot table, compare Figure \ref{fig:8-5}. Then $K$ has a Coxeter quotient with graph $$A_3 =\coxtwothreethree$$ which is isomorphic to the permutation group $S_4$.
Note that by the Wirtinger algorithm, the reflection quotient (defined in Section \ref{subsec:reflection-quotient}) has a presentation
$$r(8_5) = \langle a, b, c\; | \; babc(ba)^2bc(ba)^4, babc(ba)^4cbabc(ab)^2a \rangle^{(2)}.$$
%TODO check this
These relations are satisfied in the Coxeter group
$$W = \langle a, b, c \; | \; (ab)^2, (ac)^3, (bc)^3 \rangle^{(2)}.$$
Thus, $W$ is a quotient of $\pi_1(S^3 \setminus 8_5)$.
\end{example}

Note that there exist presentations of the knot group of $8_5$, for example, any presentation involving more than three meridians, such that the above method does not work. It is thus difficult to prove in general that a fixed link $L$ does not admit a Coxeter quotient isomorphic to a specific Coxeter group $W$.



\subsection{List of Coxeter Knots}\label{subsec:list-of-quotients}
The following list of Coxeter knots in Rolfsen's table \cite{rolfsen2003} was found using the following algorithm. First, compute a presentation of the reflection quotient using the Wirtinger algorithm, modified such that the presentation does not use more generators than the bridge index of the knot in question. Then, use some solution of the word problem in Coxeter groups to find all Coxeter quotients that map generating meridians to generating reflections. Note that this algorithm may not detect all Coxeter knots.

Because all $2$-bridge knots are Coxeter (see Section \ref{subsec:rank-two}), Table \ref{tab:cox-quotients} consists of all $3$-bridge knots in Rolfsen's table that were found to be Coxeter by the above algorithm. We include up to nine crossings.

\begin{table}[htb]
\centering
\begin{minipage}[t]{0.45\textwidth}
\centering
\begin{tabular}[t]{c|c}
Knot & Coxeter Quotients \\
\hline
$8_5$ & \coxtwothreethree \\
$8_{10}$ & \coxtwothreethree \\
$8_{15}$ & \coxtwothreethree \\
$8_{19}$ & \coxtwothreethree \\
$8_{20}$ & \coxtwothreethree \\
$8_{21}$ & \coxtwothreethree \\
$9_{16}$ & \coxtwothreethree \\
$9_{22}$ & \coxathreetype{$5$} \\
$9_{24}$ & \coxtwothreethree \\
$9_{25}$ & \coxathreetype{$5$} \\
$9_{28}$ & \coxtwothreethree \\
$9_{30}$ & \coxathreetype{$5$} \\
\end{tabular}
\end{minipage}%
\begin{minipage}[t]{0.55\textwidth}
\centering
\begin{tabular}[t]{c|c}
Knot & Coxeter Quotients \\
\hline
\verticalcenter{$9_{35}$}\rule{0pt}{4ex} & \verticalcenter{\verticalcenter{\coxtwothreethree} and \verticalcenter{\coxthreethreethree}} \\
\verticalcenter{$9_{36}$} & \coxathreetype{$5$} \\
\verticalcenter{$9_{37}$} &
\verticalcenter{\verticalcenter{\coxtwothreethree} and
\verticalcenter{\coxthreethreethree}} \\
\verticalcenter{$9_{40}$} & $\;\;\,$\verticalcenter{\coxtwothreethree} and \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$9_{42}$} & \coxathreetype{$5$} \\
\verticalcenter{$9_{43}$} & \coxathreetype{$5$} \\
\verticalcenter{$9_{44}$} & \coxathreetype{$5$} \\
\verticalcenter{$9_{45}$} & \coxathreetype{$5$} \\
\verticalcenter{$9_{46}$} &
\verticalcenter{\verticalcenter{\coxtwothreethree} and
\verticalcenter{\coxthreethreethree}} \\
\verticalcenter{$9_{48}$} &
\verticalcenter{\verticalcenter{\coxtwothreethree} and
\verticalcenter{\coxthreethreethree}} \\
\end{tabular}
\end{minipage}
\caption{List of Coxeter knots with bridge index $3$}
\label{tab:cox-quotients}
\end{table}

$3$-bridge knots that were not found to have a rank $3$ Coxeter quotient but have yet to be proven to not admit one include $8_{16}, 8_{17}, 8_{18}, 9_{29}, 9_{32}, 9_{33}, 9_{34}, 9_{38}, 9_{39}, 9_{41}, 9_{47}$ and $9_{49}$.

Data concerning knots of crossing number $10$ can be found in Appendix \ref{sec:data}.

\subsection{Meridional Rank}\label{subsec:meridional-rank}
For a link $L \subset S^3$ we define its \textit{Coxeter rank}, abbreviated $\text{cr } L$, to be the maximal number $n$ such that $L$ has a Coxeter quotient of rank $n$. Abbreviating the meridional rank of $L$ by $\text{mr }L$ and the bridge index of $L$ by $\text{bi } L$, we have the following.

\begin{theorem}
Let $L \subset S^3$ be any link. Then we have $\textup{cr }L \leq \textup{mr }L \leq \textup{bi } L$.
\end{theorem}

\begin{proof}
The inequality $\textup{mr } L \leq \text{bi } L$ is well-known. Moreover, $\text{cr } L \leq \text{mr } L$, is a direct consequence of \cite[Lemma 2.1]{felikson2009}.
\end{proof}

Let us refer to a link $L \subset S^3$ that has a Coxeter quotient of rank $n = \text{bi } L$ as a \textit{Coxeter link}. Then we immadiately obtain:

\begin{corollary}\label{cor:coxeter-links-meridional-rank}
Coxeter links satisfy the meridional rank conjecture.
\end{corollary}

Another application of the techniques we have developed so far lies in the following.

\begin{theorem}\label{thm:connected-sums-coxeter-rank}
Let $K$ and $K'$ be knots. Then $\textup{cr } K\#K' \geq \textup{cr } K + \textup{cr } K' - 1$.
\end{theorem}

\begin{proof}
Let $W$ and $W'$ be Coxeter quotients of $K$ and $K'$, respectively. First we choose diagrams of $K$ and $K'$ such that the generators of $\pi(K)$ and $\pi(K')$ that get mapped to generating reflections of $W$ and $W'$ are diagram meridians. Let $s \in \pi(K)$ and $s' \in \pi(K')$ each be one of those diagram meridians.

Now observe that $\pi(K\#K')$ is of the form $\pi(K) * \pi(K') / ss'$. Thus, we can explicitly write down a Coxeter quotient of $K\#K'$ as follows. Let $\Gamma$ and $\Gamma'$ be the Coxeter graphs associated to $W$ and $W'$. Then there is a Coxeter quotient of $K\#K'$ with graph
\begin{center}
\begin{tikzpicture}
\draw[dashed] (0.85, 0.15) -- (0.15, 0.85);
\draw[dashed] (-0.15, 0.85) -- (-0.85, 0.15);
\draw (0.8, 0) -- (-0.8, 0);

\node at (0, 1) {$s$};
\node at (-1, 0) {$\Gamma$};
\node at (1, 0) {$\Gamma'$};
\node at (0, 0.2) {$\infty$};
\end{tikzpicture}
\end{center}
which has rank $\text{rk } W + \text{rk } W' - 1$. 
\end{proof}

\begin{corollary}
Knots of Coxeter rank two are prime.
\end{corollary}

\begin{proof}
This follows directly from the facts that bridge index one knots are prime and that the bridge index satisfies the same inequality, see Proposition \ref{prop:bridge-index-connected-sum}.
\end{proof}

\begin{corollary}
There are knots of arbitrarily high meridional rank.
\end{corollary}

\begin{proof}
Just take connected sums of your favorite two-bridge knot.
\end{proof}

\begin{corollary}
Connected sums of Coxeter knots are Coxeter knots.
\end{corollary}

\begin{proof}
Let $J, K \subset S^3$ be arbitrary knots. Then we have already shown that $\text{bi } J\#K = \text{bi } J + \text{bi } K - 1$ and $\text{cr } J\#K \leq \text{bi } J\#K$. If $J$ and $K$ are both Coxeter knots then equality immediately follows from Theorem \ref{thm:connected-sums-coxeter-rank}.
\end{proof}

\subsection{Rank Two Quotients}\label{subsec:rank-two}
In this section we have a particularly close look at dihedral quotients of link groups. As we shall see, this is closely related to a popular notion in the literature, described for example in \cite{przytycki1998}. 

Let $L$ be a link. We will refer to a homomorphism $c: \pi(L) \rightarrow D_n$ mapping all meridians of $L$ to reflections in $D_n$ as a \textit{Fox $n$-coloring}. Note that a surjective Fox $n$-coloring is a dihedral quotient of $L$. We will call a Fox $n$-coloring $c$ \textit{non-trivial} if the image of $c$ contains more than one reflection in $D_n$, and we will call a link $L$ \textit{Fox $n$-colorable} if $L$ admits a non-trivial Fox $n$-coloring. Note that any link admits trivial Fox $n$-colorings for all $n$.

\begin{example}[Fox $3$-colorings]
Let $a, b, c$ be the reflections of $D_3$. Then a Fox $3$-coloring of $L$ is just a labeling of the arcs in a diagram of $L$ such that at any crossing either only one symbol or all three symbols appear.

The reader may convince themselves of the fact that the trefoil knot in Figure \ref{fig:trefoil} is Fox $3$-colorable, whereas the figure-8 knot in Figure \ref{fig:figure-8} is not.

\begin{figure}[ht]
\centering
\begin{minipage}{0.5\textwidth}
 \centering
\begin{tikzpicture}
\clip (-2, -1.6) rectangle (2,2.7);
\begin{knot}[clip width = 5, consider self intersections = true, flip crossing = 2]

\strand[black, thick] (0,2) .. controls +(2.2,0) and +(120:-2.2) .. (210:2) .. controls +(120:2.2) and +(60:2.2) .. (-30:2) .. controls +(60:-2.2) and +(-2.2,0) .. (0,2);
\end{knot}
\end{tikzpicture}
\caption{The Trefoil Knot}
\label{fig:trefoil}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\centering
\begin{tikzpicture}
\clip (-2, -2.5) rectangle (2, 1.8);
\begin{knot}[consider self intersections = true, ignore endpoint intersections=false, clip width = 5, flip crossing = 2]
\strand[thick] (0, 1.5) .. controls +(1.5, 0) and +(0, 1) .. (-0.5, -1) .. controls +(0, -1) and +(0, -2.6) .. (1.5, -1) .. controls +(0, 2.6) and +(0, 2.6) .. (-1.5, -1) .. controls +(0, -2.6) and +(0, -1) .. (0.5, -1) .. controls +(0, 1) and +(-1.5, 0) .. (0, 1.5);
\end{knot}
\end{tikzpicture}
\caption{The Figure-Eight Knot}
\label{fig:figure-8}
\end{minipage}
\end{figure}
\end{example}

Let $n$ be a prime number. We will now present an algorithm to check whether a given link $L$ is $n$-colorable. First we make the following identification of the set of reflections with $\mathbb{Z}_n$. Write $D_n = \langle a, b \; | \; (ab)^n \rangle$. Then the set $R$ of reflections is the set of elements of the form $(ab)^ka$. We will identify this reflection with the element $k$ in $\mathbb{Z}_p$.

Under this identification, the Wirtinger relation at any crossing reads $2k = i + j$, see Figure \ref{fig:wirtinger-dihedral}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{knot}[clip width = 5, flip crossing = 1]
\strand[thick] (-2, -2) -- (2, 2);
\strand[thick] (-2, 2) -- (2, -2);
\end{knot}
\node at (-1, -1) {\contour{white}{$i$}};
\node at (1, 1) {\contour{white}{$j$}};
\node at (-1, 1) {\contour{white}{$k$}};
\node at (0, -2) {$2k = i + j$};
\end{tikzpicture}
\caption{The Wirtinger relation at a crossing after identification of diagram meridians with $\mathbb{Z}_p$}
\label{fig:wirtinger-dihedral}
\end{figure}

Indexing the set of diagram meridians and the set of crossings in some manner we can interpret this as a system of linear equations over $\mathbb{Z}$. Let us call the matrix of this system $\widehat{C}$. Note that this system admits trivial solutions, namely the ones assigning the same element of $\mathbb{Z}$ to all diagram meridians. Modding out by this set of solutions corresponds to deleting a row and a column of $\widehat{C}$ to obtain what we will call the \textit{coloring matrix} $C$.

\begin{lemma}
Let $L$ be any link and $n$ be prime. Then $L$ is Fox $n$-colorable if and only if $n$ divides $\det C$, where $C$ is the coloring matrix of $L$.
\end{lemma}

\begin{proof}
The condition for the linear system described above to have non-trivial solutions is for $C$ to be singular over $\mathbb{Z}_n$, which is obviously equivalent to $n$ dividing $\det C$ as a matrix with integer coefficients.
\end{proof}

We will refer to the determinant $\det C$ simply as the \textit{determinant} of $L$, written $\det L$. In the literature the determinant of $L$ is usually defined to be its Alexander polynomial evaluated at $-1$, but it turns out that these definitions are actually equivalent.

\begin{example}
Consider the Trefoil $K$ indexed as in Figure \ref{fig:trefoil-labeled-for-coloring}.
\begin{figure}[ht]
\centering
\begin{tikzpicture}
\clip (-2, -1.6) rectangle (2,2.7);
\begin{knot}[clip width = 5, consider self intersections = true, flip crossing = 2]

\strand[black, thick] (0,2) .. controls +(2.2,0) and +(120:-2.2) .. (210:2) .. controls +(120:2.2) and +(60:2.2) .. (-30:2) .. controls +(60:-2.2) and +(-2.2,0) .. (0,2);
\end{knot}
\node at (0, 2) {\contour{white}{$i$}};
\node at (210:2) {\contour{white}{$k$}};
\node at (-30:2) {\contour{white}{$j$}};

\node at (0, -1.1) {$1$};
\node at (-1, 0.6) {$3$};
\node at (1, 0.6) {$2$};
\end{tikzpicture}
\caption{The Trefoil Knot with labels}
\label{fig:trefoil-labeled-for-coloring}
\end{figure}

Then the linear equations read $2i = j + k$, $2j = i + k$ and $2k = i + j$, corresponding to the matrix
$$\widehat{C} = \left(\begin{matrix}
2 & -1 & -1 \\
-1 & 2 & -1 \\
-1 & -1 & 2
\end{matrix}\right).$$
Deleting from $\widehat{C}$ the last row and the last column we obtain the coloring matrix
$$C = \left( \begin{matrix}
2 & -1 \\
-1 & 2
\end{matrix} \right),$$
yielding that $\det K = 3$. Note that this agrees with the previous observation that $K$ is Fox $3$-colorable.
\end{example}

We are now ready to eliminate $2$-bridge knots from all our discussions with the techniques developed here. The key to this lies in the following.

\begin{theorem}
Let $K$ be a $2$-bridge link. Then $\det L > 1$.
\end{theorem}
%TODO prove and cite

\begin{corollary}
All $2$-bridge links are Coxeter.
\end{corollary}

\subsection{Realization}
In this section we are going to show that many Coxeter groups are Coxeter quotients of knots. In fact, \textit{all} Coxeter groups are Coxeter quotients of links.

\begin{proposition}\label{prop:trivial-realization}
Let $L$ be the trivial link on $n$ components. Then the link group $\pi(L)$ is free on $n$ generators which are meridians. In particular, any Coxeter group $W$ is a Coxeter quotient of $\pi(L)$.
\end{proposition}

Since this is a little underwhelming we will try to do better. The following construction is essentially due to Brunner \cite{brunner1992}.

Let $\Gamma$ be any Coxeter graph, this time with edges labeled $2$ for commuting generators and no edge for no relations (contrary to the convention above). If $\Gamma$ is not planar, choose a maximal planar subgraph instead of $\Gamma$ and fix an embedding of $\Gamma$ into the plane.

Now consider the dual graph $\Gamma^*$ of $\Gamma$ whose vertices are the faces of $\Gamma$, with edges weighted $m$ connecting vertices $s, t$ if and only if there is an edge labeled $m$ separating the faces of $\Gamma$ corresponding to $s, t$. Note that $\Gamma^*$ is not necessarily simple, even if $\Gamma$ is (e.g., if $\Gamma$ is a tree).

We now interpret $\Gamma^*$ as a set of instructions how to construct a surface $S$ whose boundary will be a link $L(\Gamma^*)$ admitting a Coxeter quotient isomorphic to the Coxeter group corresponding to $\Gamma$. First, blow up the vertices of $\Gamma^*$ to disks. Now replace each edge labelled $m$ between disks by bands with $m$ twists. This procedure is illustrated in Figure \ref{fig:brunners-construction}.

\begin{figure}[htb]
\centering
\begin{minipage}{0.37\textwidth}
\centering
\begin{tikzpicture}[scale = 0.75]
\draw[thick] (0, 0) -- (4, 0);
\draw[thick] (0, 0) .. controls +(45:2) and +(315:-2) .. (4, 0);
\draw[thick] (0, 0) .. controls +(315:2) and +(45:-2) .. (4, 0);
\draw[thick] (-0.5, 0) circle (0.5);

\draw[fill = black] (0, 0) circle (0.1);
\draw[fill = black] (4, 0) circle (0.1);

\node at (2, 1.23) {\tiny{$2$}};
\node at (2, 0.2) {\tiny{$3$}};
\node at (2, -0.9) {\tiny{$4$}};
\node at (-1.2, 0) {\tiny{$2$}};
\end{tikzpicture}
\end{minipage}%
\begin{minipage}{0.63\textwidth}
\centering
\begin{tikzpicture}[scale = 0.45]
\draw[thick] (0, 0) circle (2);
\draw[thick] (12, 0) circle (2);
\filldraw[color=white] (0, 0.95) -- (4, 0.95) -- (4, 1.45) --								  (0, 1.45);
\filldraw[color=white] (0, 0.25) -- (4, 0.25) -- (4, -0.25) --
							  (0, -0.25);
\filldraw[color=white] (0, -0.95) -- (4, -0.95) -- (4, -1.45)
							  -- (0, -1.45);
\filldraw[color=white] (0, 1.85) -- (-2, 1.85) -- (-2, 1.35)
								-- (0, 1.35);
\filldraw[color=white] (0, -1.85) -- (-2, -1.85) -- (-2, -1.35)
								-- (0, -1.35);
\filldraw[color=white] (12, 0.95) -- (8, 0.95) -- (8, 1.45) --								  (12, 1.45);
\filldraw[color=white] (12, 0.25) -- (8, 0.25) -- (8, -0.25) --
							  (12, -0.25);
\filldraw[color=white] (12, -0.95) -- (8, -0.95) -- (8, -1.45)
							  -- (12, -1.45);

\begin{knot}[clip width = 5, ignore endpoint intersections=false,
clip radius=2pt,
flip crossing/.list = {1, 4, 7, 9, 10}]

\strand[thick] (0, 0.9) -- (5, 0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				 .. (6, 1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				 .. (7, 0.9) -- (12, 0.9);
				 
\strand[thick] (0, 1.5) -- (5, 1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				 .. (6, 0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				 .. (7, 1.5) -- (12, 1.5);

\strand[thick] (0, 0.3) -- (4.5, 0.3) .. controls +(0.3, 0) and +(-0.3, 0)
			   .. (5.5, -0.3) .. controls +(0.3, 0) and +(-0.3, 0)
			   .. (6.5, 0.3) .. controls +(0.3, 0) and +(-0.3, 0)
			   .. (7.5, -0.3) -- (12, -0.3);
\strand[thick] (0, -0.3) -- (4.5, -0.3) .. controls +(0.3, 0) and +(-0.3, 0)
				.. (5.5, 0.3) .. controls +(0.3, 0) and +(-0.3, 0)
				.. (6.5, -0.3) .. controls +(0.3, 0) and +(-0.3, 0)
				.. (7.5, 0.3) -- (12, 0.3);
				
\strand[thick] (0, -0.9) -- (4, -0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (5, -1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (6, -0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (7, -1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (8, -0.9) -- (12, -0.9);
\strand[thick] (0, -1.5) -- (4, -1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (5, -0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (6, -1.5) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (7, -0.9) .. controls +(0.3, 0) and +(-0.3, 0)
				  .. (8, -1.5) -- (12, -1.5); 

\strand[thick] (0, 1.9) -- (-3, 1.9) .. controls +(-0.5, 0) and +(0, 0.5)
				 .. (-4, 1) .. controls +(0, -0.3) and +(0, 0.3)
				 .. (-3.4, 0) .. controls +(0, -0.3) and +(0, 0.3)
				 .. (-4, -1) .. controls +(0, -0.5) and +(-0.5, 0)
				 .. (-3, -1.9) -- (0, -1.9);
\strand[thick] (0, 1.3) -- (-3, 1.3) .. controls +(-0.15, 0) and +(0, 0.15)
				 .. (-3.4, 1) .. controls +(0, -0.3) and +(0, 0.3)
				 .. (-4, 0).. controls +(0, -0.3) and +(0, 0.3)
				 .. (-3.4, -1) .. controls +(0, -0.15) and +(-0.15, 0)
				 .. (-3, -1.3) -- (0, -1.3);
\end{knot}

\filldraw[color=white] (0, 0) circle (1.95);
\filldraw[color=white] (12, 0) circle (1.95);
\end{tikzpicture}\end{minipage}
\caption{Brunner's construction producing from $\Gamma^*$ (left) a link (right)}
\label{fig:brunners-construction}
\end{figure}

\begin{theorem}
The link constructed by Brunner's construction starting with a graph $\Gamma$ yields a link that has a Coxeter quotient isomorphic to the Coxeter group $W$ corresponding to $\Gamma$.
\end{theorem}

%TODO proof

This is much more interesting than the construction in Proposition \ref{prop:trivial-realization}. Indeed, we are almost ready to answer the following question: what Coxeter groups are Coxeter quotients of knots? But first, we need the following lemma.

\begin{lemma}\label{lem:tree->knot}
Let $\Gamma$ be a Coxeter graph with no cycles, i.e., a tree, whose edges are all odd. Then Brunner's construction applied to $\Gamma$ yields a knot.
\end{lemma}

\begin{proof}
Note that the dual graph of a tree is a wedge of circles, that is, a graph with only one vertex. So Brunner's construction yields a disk with bands with an odd number of twists attached. We will prove by induction on the number of bands that the boundary of this surface $S$ has only one component.

First note that if there are no bands attached, the boundary of the disk is the unknot. This concludes the base case of the induction. Now  fix an innermost band $B$, and start at the point $p$ on the boundary of $S$ that lies immediately to the left of $B$. Let $q$ be the point on $S$ that lies immediately to the right of $B$. Then tracing the boundary as in Figure \ref{fig:tracing-band} shows that there exists a path from $p$ to $q$ that only passes through $B$.

\begin{figure}[htb]
\centering
\begin{tikzpicture}
\begin{knot}[clip width = 5, consider self intersections = true]
\clip (-0.2, -0.2) rectangle (11.2, 2.2);
\strand[thick] (2, 0) -- (4, 0) -- (4, 1)
				.. controls +(0, 1) and +(-1, 0) .. (5, 2)
				.. controls +(0.25, 0) and +(-0.25, 0) .. (6, 1.5)
				.. controls +(0.5, 0) and +(0, 0.5) .. (6.5, 1)
				-- (6.5, 0) -- (4.5, 0) -- (4.5, 1)
				.. controls +(0, 0.5) and +(-0.5, 0) .. (5, 1.5)
				.. controls +(0.25, 0) and +(-0.25, 0) .. (6, 2)
				.. controls +(1, 0) and +(0, 1) .. (7, 1)
				-- (7, 0) -- (9, 0);
\end{knot}
\node at (3.75, 0.25) {\contour{white}{$p$}};
\node at (7.25, 0.25) {\contour{white}{$q$}};
\draw[fill = black] (4, 0) circle (0.06);
\draw[fill = black] (7, 0) circle (0.06);
\end{tikzpicture}
\caption{Tracing a band arising from Brunner's construction on a tree. Note that the situation is the same if instead of one twist there are an odd number of twists in $B$.}
\label{fig:tracing-band}
\end{figure}

Contracting this path yields a surface with one band less. By the induction hypothesis the boundary of this is a knot. Thus, so is the boundary of $S$.
\end{proof}

\begin{theorem}
Let $W$ be a Coxeter group. Then $W$ is a Coxeter quotient of a knot if and only if the set $T$ of reflections in $W$ is a single conjugacy class.
\end{theorem}

\begin{proof}
Let $\Gamma$ be the graph of $W$, and let $\Gamma_0$ be the subgraph of $\Gamma$ only consisting of the odd-weighted edges as in Section \ref{subsec:conjugacy-classes}. Since all meridians in a knot group are conjugate it follows that if $\Gamma_0$ is disconnected, then $W$ is not a Coxeter quotient of a knot.

Conversely, if $\Gamma_0$ is connected, apply Brunner's construction to $\Gamma_0$. This is a knot by \ref{lem:tree->knot}. Moreover it has a Coxeter quotient isomorphic to the Coxeter group $\widetilde{W}$ corresponding to the graph $\Gamma_0$ whose non-edges are replaced by edges labeled $\infty$. This group itself has a Coxeter quotient isomorphic to $W$.
\end{proof}

\newpage

\section{Torus Knots}\label{sec:torus-knots}
The motto of this section will be that \textit{torus knots tend to admit few Coxeter quotients}. This is evident first in Section \ref{subsec:odd-weights}, where we show that an infinite class of torus knots does not admit any non-trivial Coxeter quotients, further adding to the well-known statement that \textit{knots of determinant one admit poor representation theory}.

\subsection{Preliminaries}
\begin{proposition}
Let $p, q$ be positive integers. Then we have that the bridge index of the $(p, q)$-torus knot is $p$. In particular, the $(p, q)$-torus knot does not admit any Coxeter quotients of rank higher than $p$.
\end{proposition}
%TODO prove

\begin{proposition}
Let $p < q$ be positive integers. Then
$$\det T(p, q) = \begin{cases}
1 & \textup{if } p \textup{ and } q \textup { are odd,} \\
... & \\
... & \\
\end{cases} $$
\end{proposition}
%TODO state and prove

\subsection{Odd Weights}\label{subsec:odd-weights}
As with many things when considering Torus knots, the qualitative features as far as Coxeter quotients go depend heavily on the weights $p, q$ of the $(p, q)$-torus knots. The reason for just considering odd weights lies in the fact that if $p$ and $q$ are odd, the $(p, q)$-torus knot has determinant one. The reason for this lies in the following well-known result.
%TODO cite

\begin{theorem}
Let $p, q$ be odd positive integers. Then the Alexander polynomial of $K = T(p, q)$ is
$$\Delta_K(t) = \frac{(t^{pq}-1)(t-1)}{(t^q-1)(t^p-1)}.$$
\end{theorem}

Because the determinant of a knot is its Alexander polynomial evaluated at $-1$, we immediately obtain the desired result.

\begin{corollary}
Let $p, q$ be odd. Then the $(p, q)$-torus has determinant one.
\end{corollary}

In Section \ref{subsec:rank-two} we have seen that this implies that torus knots with odd weights do not admit dihedral quotients. This brings us one step closer to the claim that torus knots with odd weights have very few Coxeter quotients. To illustrate our strategies, let us first fix $p = 3$.

\begin{theorem}\label{thm:p=3}
Let $q$ be an odd positive integer such that $q$ has no prime factor less than or equal to $5$. Then the $(3, q)$-torus knot does not admit any non-trivial Coxeter quotients.
\end{theorem}

Before proving this, we need a few lemmas.

\begin{lemma}
The only irreducible finite Coxeter groups with abelianization $\mathbb{Z}_2$ of rank three are $\mathbb{Z}_2 \times A_5$ and $S_4$.
\end{lemma}

\begin{proof}
This follows directly from the classification of finite irreducible Coxeter groups, see Table \ref{tab:classification}.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:p=3}]
It suffices to prove that $K = T(3, q)$ does not admit any rank three Coxeter quotients. Toward a contradiction, suppose $W$ is a Coxeter quotient of $K$ of rank three. Since $K$ is a knot we have that $W$ is irreducible. We will now consider two cases.

First, if $W$ is infinite, then $W$ has trivial center. Let $G = \pi(K)$ and consider the quotient map $\varphi: G \rightarrow W$. Recall that this means that for any meridian $m$ of $K$ we have that $\varphi(m)$ is a reflection in $W$. Since $\varphi$ is surjective we have that the center of $G$ is mapped into the center of $W$, and is thus sent to the identity. Recall that $G$ has a presentation
$$G = \langle a, b \; | \; a^3 = b^q \rangle$$
where $a$ and $b$ are meridian and longitude of the torus on which $K$ lies, respectively. Moreover, the center of $G$ is generated by the element $a^p = b^q$, which is a composition of an odd number of diagram meridians of $K$ since both $p$ and~$q$ are odd. But this is a contradiction: the image of $a^p = b^q$ in $W$ under~$\varphi$ is orientation-preserving because it is the identity, and orientation-reversing because it is the product of an odd number of reflections.

Finally, suppose $W$ is finite. Then $W$ is isomorphic to either $S_4$ or $\mathbb{Z}_2 \times A_5$ since $K$ is a knot. Note that $\varphi(b)$ has order dividing $q$, but by assumption $q$ has no divisor that is also a divisor of the order of $W$, which is either $24 = 2^3 \cdot 3$ or $120 = 2^3 \cdot 3 \cdot 5$.
%There are no infinite ones because $\pi(K)$ has non-trivial center and no finite ones because neither $S_4$ nor $\mathbb{Z}_2 \times A_5$ have elements of order the prime factor greater than or equal to $7$.
\end{proof}

A very similar Theorem is true for $p \geq 5$, as another close look at the classification of finite irreducible Coxeter groups in Table \ref{tab:classification} shows.

\begin{lemma}
No irreducible finite Coxeter group of rank $p \geq 5$ has an element of order $q > p$, where $q$ is prime.
\end{lemma}

\begin{theorem}
Let $5 \leq p < q$ be any odd coprime integers such that $q$ has no prime factor less than or equal to $p$. Then the $(p, q)$-torus knot does not admit any non-trivial Coxeter quotients.
\end{theorem}

\begin{proof}
This is completely analogous to Theorem \ref{thm:p=3}.
\end{proof}

\subsection{Close Weights}
This section contains an upshot showing that some torus knots in fact do have Coxeter quotients, namely the $(n, n + 1)$-torus knots.

\begin{example}[$n=4$]
Consider the braid representation of the $(4, 5)$-torus knot in Figure~\ref{fig:torus45}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale = 1.15]
\begin{knot}[clip width = 5, flip crossing/.list = {4, 5,6, 10, 11, 12}]
\strand[thick] (0, -0.5) -- (0, 0);
\strand[thick] (1, -0.5) -- (1, 0);
\strand[thick] (2, -0.5) -- (2, 0);
\strand[thick] (3, -0.5) -- (3, 0);

\strand[thick] (0, 0) .. controls +(0, 1) and +(0, -1) .. (3, 2);
\strand[thick] (1, 0) .. controls +(0, 1) and +(0, -1) .. (0, 2);
\strand[thick] (2, 0) .. controls +(0, 1) and +(0, -1) .. (0, 4);
\strand[thick] (3, 0) .. controls +(0, 1) and +(0, -1) .. (0, 6);

\strand[thick] (0, 2) .. controls +(0, 1) and +(0, -1) .. (3, 4);
\strand[thick] (0, 4) .. controls +(0, 1) and +(0, -1) .. (3, 6);
\strand[thick] (3, 2) .. controls +(0, 1) and +(0, -1) .. (0, 8);
\strand[thick] (3, 4) .. controls +(0, 1) and +(0, -1) .. (0, 10);

\strand[thick] (0, 6) .. controls +(0, 1) and +(0, -1) .. (3, 8);
\strand[thick] (0, 8) .. controls +(0, 1) and +(0, -1) .. (3, 10);

\strand[thick] (3, 6) .. controls +(0, 1) and +(0, -1) .. (1, 10);
\strand[thick] (3, 8) .. controls +(0, 1) and +(0, -1) .. (2, 10);



\strand[thick] (0, 10) -- (0, 10.5);
\strand[thick] (1, 10) -- (1, 10.5);
\strand[thick] (2, 10) -- (2, 10.5);
\strand[thick] (3, 10) -- (3, 10.5);
\end{knot}

\node at (0, 0) {\contour{white}{$a$}};
\node at (0, 2) {\contour{white}{$b$}};
\node at (0, 4) {\contour{white}{$c$}};
\node at (0, 6) {\contour{white}{$d$}};
\node at (0, 8) {\contour{white}{$dcbabcd$}};
\node at (0, 10) {\contour{white}{$dcbababcd$}};

\node at (1.2, 7.6) {\contour{white}{$dcbcd$}};
\node at (1.8, 8.4) {\contour{white}{$dcd$}};
\node at (1.8, 6.4) {\contour{white}{$cbc$}};
\node at (1.8, 4.4) {\contour{white}{$bab$}};
\node at (1.2, 5.65) {\contour{white}{$cbabc$}};
\node at (1.08, 9.6) {\contour{white}{$dcbabcbabcd$}};
\node at (2, 10.2) {\contour{white}{$dcbabcdcbabcd$}};

\node at (1, 0) {\contour{white}{$aba$}};
\node at (1.2, 3.6) {\contour{white}{$bcb$}};
\node at (2, 0) {\contour{white}{$abcba$}};
\end{tikzpicture}
\caption{The case $n = 4$}
\label{fig:torus45}
\end{figure}

Considering the first three strands we obtain a presentation of the reflection quotient of $K$, namely
$$r(K) = \langle a, b, c, d \; | \; adcbababcd, abadcbabcbabcd, abcbadcbabcdcbabcd \rangle^{(2)}.$$
The rules $a \mapsto (1 \; 2)$, $b \mapsto (2 \; 3)$, $c \mapsto (3 \; 4)$, $d \mapsto (4 \; 5)$ extend to a surjective homomorphism $r(K) \rightarrow S_5$, because all relators are mapped to the identity.
\end{example}

\begin{theorem}
Let $n \geq 2$ be an integer. Then the $(n, n+1)$-torus knot admit a Coxeter quotient isomorphic to $S_{n+1}$. In particular, $(n, n+1)$-torus knots are Coxeter.
\end{theorem}

\begin{proof} Similarly as before we consider the braid representation of the $(n, n+1)$-torus knot in Figure \ref{fig:torusnn+1}. The first $n-1$ strands give us the following defining relations.
\begin{itemize}
\setlength\itemsep{0em}
\item $s_1 = s_n \cdots s_1 s_2 s_1 \cdots s_n$
\item $s_1s_2s_1 = s_n \cdots s_1 s_2 s_3 s_2 s_1 \cdots s_n$
\item \dots
\item $s_1 \cdots s_i \cdots s_1 = s_n \cdots s_1 \cdots s_{i+1} \cdots s_1 \cdots s_n$ for $1 \leq i \leq n-1$
\item \dots
\item $s_1 \cdots s_{n-1} \cdots s_1 = s_n \cdots s_1 \cdots s_n \cdots s_1 \cdots s_n$
\end{itemize}
These relations are all satisfied under the map $s_i \mapsto (i \;\;\; i+1)$. To see this, compute 
$$s_{i+1} \cdots s_1 \cdots s_{i+1} \cdots s_1 \cdots s_{i+1} \mapsto (1 \;\; i+1)$$
which is fixed by conjugation with $s_j$ for $j > i$. So the right hand side of the relation is equal to $(1 \; \; i + 1)$. But $s_1 \cdots s_{i-1} \mapsto (1 \; \cdots \; i)$, which conjugates $s_i$ to $(1 \; \; i + 1)$, so the left hand side is also equal to $(1 \; \; i + 1)$. 
\end{proof}

\begin{figure}
\centering
\begin{tikzpicture}[yscale=0.95, xscale=1.15]
\begin{knot}[clip width = 5]
\clip (-1.2, -0.5) rectangle (9.2, 18.5);
\strand[thick] (0, 0) .. controls +(0,1) and +(30:-1) .. (2, 2);
\strand[thick, dashed] (2, 2) .. controls +(30:1) and +(30:-1) .. (6, 4);
\strand[thick] (6, 4) .. controls +(30:1) and +(0, -1) .. (8, 6);
\strand[thick] (1, 0) .. controls +(0, 1) and +(0, -1) .. (0, 2);

\strand[thick] (0, 2) .. controls +(0,1) and +(30:-1) .. (2, 4);
\strand[thick, dashed] (2, 4) .. controls +(30:1) and +(30:-1) .. (6, 6);
\strand[thick] (6, 6) .. controls +(30:1) and +(0, -1) .. (8, 8);
\strand[thick] (2, 0) .. controls +(0, 1) and +(0, -1) .. (0, 4);

\strand[thick] (0, 4) .. controls +(0,1) and +(30:-1) .. (2, 6);
\strand[thick, dashed] (2, 6) .. controls +(30:1) and +(30:-1) .. (6, 8);

\strand[thick] (0, 6) .. controls +(0, 1) and +(30:-1) .. (2, 8);

\strand[thick] (6, 0) -- (6, 2);
\strand[thick] (7, 0) -- (7, 3);
\strand[thick] (7, 3) .. controls +(0, 1) and +(120:-1) .. (6, 5);
\strand[thick] (8, 0) -- (8, 4);
\strand[thick] (8, 4) .. controls +(0, 1) and +(120:-1) .. (6, 7);
\strand[thick] (8, 6) .. controls +(0, 1) and +(120:-1) .. (7, 8);

\strand[thick] (2, 6.5) -- (1, 8);
\strand[thick] (2, 2.5) .. controls +(120:1) and +(0, -1) .. (0, 6);
\strand[thick] (2, 4.5) .. controls +(120:1) and +(0, -1) .. (0, 8);

\strand[thick] (0, 10) .. controls +(0,1) and +(30:-1) .. (2, 12);
\strand[thick, dashed] (2, 12) -- (6, 14);
\strand[thick] (6, 14) .. controls +(30:1) and +(0, -1) .. (8, 16);


\strand[thick] (0, 12) .. controls +(0,1) and +(30:-1) .. (2, 14);
\strand[thick, dashed] (2, 14) -- (6, 16);
\strand[thick] (6, 16) .. controls +(30:1) and +(0, -1) .. (8, 18);
\strand[thick] (1, 10) .. controls +(120:1) and +(0, -1) .. (0, 12);
\strand[thick] (2, 10) .. controls +(120:1) and +(0, -1) .. (0, 14);
\strand[thick] (0, 14) -- (0, 18);

\strand[thick] (2, 12.5) .. controls +(120:1) and +(0,-1) .. (1, 15) -- (1, 18);
\strand[thick] (2, 16) -- (2, 18);

\strand[thick, dashed] (2.3, 10.15) -- (6, 12);
\strand[thick] (6, 12) .. controls +(30:1) and +(0, -1) .. (8, 14);
\strand[thick] (6, 10) .. controls +(30:1) and +(0, -1) .. (8, 12);

\strand[thick] (8, 16) .. controls +(0, 1) and +(0, -1) .. (7, 18);
\strand[thick] (8, 14) .. controls +(0, 1) and +(0, -1) .. (6, 18);
\strand[thick] (8, 12) .. controls +(0, 1) and +(120:-1) .. (6, 15.5);
\strand[thick] (8, 10) .. controls +(0, 1) and +(120:-1) .. (6, 13.5);
\strand[thick] (7, 10) -- (6, 11.5);

%tails
\strand[thick] (0, 18) -- +(0, 0.5);
\strand[thick] (1, 18) -- +(0, 0.5);
\strand[thick] (2, 18) -- +(0, 0.5);
\strand[thick] (6, 18) -- +(0, 0.5);
\strand[thick] (7, 18) -- +(0, 0.5);
\strand[thick] (8, 18) -- +(0, 0.5);

\strand[thick] (0, 0) -- +(0, -0.5);
\strand[thick] (1, 0) -- +(0, -0.5);
\strand[thick] (2, 0) -- +(0, -0.5);
\strand[thick] (6, 0) -- +(0, -0.5);
\strand[thick] (7, 0) -- +(0, -0.5);
\strand[thick] (8, 0) -- +(0, -0.5);
\end{knot}

\node at (4, 1) {\Large{$\dots$}};
\node at (4, 17) {\Large{$\dots$}};
\node at (4, 9) {\Large{$\vdots$}};

\node at (0, -0.2) {\contour{white}{$s_1$}};
\node at (0, 2) {\contour{white}{$s_2$}};
%\node at (0, 4) {\contour{white}{$s_3$}};

\node at (1, 0.2) {\contour{white}{$s_1s_2s_1$}};
%\node at (1, 2) {\contour{white}{$s_2s_3s_2$}};
%\node at(2, 0.2) {\contour{white}{$s_1s_2s_3s_2s_1$}};
\node at (6, 0.2) {\contour{white}{$s_1 \dotsm s_{n-2} \dotsm s_1$}};
\node at (7, -0.2) {\contour{white}{$s_1 \dotsm s_{n-1} \dotsm s_1$}};
%\node at (0, 10) {\contour{white}{$s_n$}};
\node at (8, 14) {\contour{white}{$s_{n-1}$}};
\node at (8, 12) {\contour{white}{$s_{n-2}$}};
%\node at (8, 10) {\contour{white}{$s_{n-3}$}};
%\node at (7.5, 13.6) {\contour{white}{$s_{n-1}s_{n-2}s_{n-1}$}};
%\node at (6.4, 13.2) {\contour{white}{$s_{n-1}s_{n-2}s_{n-3}s_{n-2}s_{n-1}$}};

\node at (8, 16) {\contour{white}{$s_n$}};
\node at (7.1, 15.6) {\contour{white}{$s_ns_{n-1}s_n$}};
\node at (0, 11.6) {\contour{white}{$s_n\dotsm s_1 \dotsm s_n$}};
\node at (1, 12) {\contour{white}{$s_n \dotsm s_2 \dotsm s_n$}};

\node at (0, 14.5) {\contour{white}{$s_n \dotsm s_1 s_ 2 s_ 1 \dotsm s_n$}};
\node at (1, 15) {\contour{white}{$s_n \dotsm s_1 s_ 2 s_3 s_2 s_1 \dotsm s_n$}};
\node at (7, 18) {\contour{white}{$s_n \dotsm s_1 \dotsm s_n \dotsm s_1 \dotsm s_n$}};

\end{tikzpicture}
\caption{The braid representation of the $(n, n+ 1)$-torus knot}
\label{fig:torusnn+1}
\end{figure}

\subsection{Other Weights}
We are nowhere close to understanding what happens in the cases not covered above. For example, the $(3, 5)$- and the $(3, 25)$-torus knots both have a $\mathbb{Z}_2 \times A_5$-quotient. Moreover, all known Coxeter quotients of Torus knots and links are finite, which is not clear from the above arguments.

\newpage

\section{Pretzel Knots}
\subsection{Preliminaries}
\subsection{A Coxeter Quotient}
\begin{theorem}\label{thm:pretzel-links-are-coxeter}
Pretzel links are Coxeter. 
\end{theorem}

\begin{proof} First consider the situation of how assigning letters to meridians propagates in 2-braids in Figure \ref{fig:elementary-twists}.
\begin{figure}[ht]
\centering
\begin{minipage}{.35\textwidth}
\centering

\begin{tikzpicture}[scale = 0.6]
\begin{knot}[clip width = 5, flip crossing = 2]

\strand[black, thick] (0, 0) .. controls +(0, 1) and +(0, -1) .. (2, 2) .. controls +(0, 1) and +(0, -1) .. (0, 4);

\strand[black, thick] (2, 0) .. controls +(0, 1) and +(0, -1) .. (0, 2) .. controls +(0, 1) and +(0, -1) .. (2, 4);

\strand[black, thick] (0, 6) .. controls +(0, 1) and +(0, -1) .. (2, 8);

\strand[black, thick] (2, 6) .. controls +(0, 1) and +(0, -1) .. (0, 8);

\end{knot}

\node at (1, 4.6) [circle, fill, inner sep=1pt]{};
\node at (1, 5) [circle, fill, inner sep=1pt]{};
\node at (1, 5.4) [circle, fill, inner sep=1pt]{};


\node at (-1.4, 0) {$x$};
\node at (3.4, 0) {$y$};
\node at (-1.4, 2) {$xyx$};
\node at (-1.4, 4) {$(xy)^2x$};
\node at (-1.4, 6) {$(xy)^{n-1}x$};
\node at (-1.4, 8) {$(xy)^nx$};
\node at (3.4, 8) {$(xy)^{n-1}x$};

\end{tikzpicture}

\end{minipage}%
\begin{minipage}{.35\textwidth}
\centering
\begin{tikzpicture}[scale = 0.6]
\begin{knot}[clip width = 5, flip crossing/.list = {1, 3}]

\strand[black, thick] (0, 0) .. controls +(0, 1) and +(0, -1) .. (2, 2) .. controls +(0, 1) and +(0, -1) .. (0, 4);

\strand[black, thick] (2, 0) .. controls +(0, 1) and +(0, -1) .. (0, 2) .. controls +(0, 1) and +(0, -1) .. (2, 4);


\strand[black, thick] (0, 6) .. controls +(0, 1) and +(0, -1) .. (2, 8);

\strand[black, thick] (2, 6) .. controls +(0, 1) and +(0, -1) .. (0, 8);

\end{knot}


\node at (1, 4.6) [circle, fill, inner sep=1pt]{};
\node at (1, 5) [circle, fill, inner sep=1pt]{};
\node at (1, 5.4) [circle, fill, inner sep=1pt]{};

\node at(-1.4, 0) {$z$};
\node at(3.4, 0) {$w$};
\node at (3.4, 2) {$wzw$};
\node at (3.4, 4) {$(wz)^2w$};
\node at (3.4, 6) {$(wz)^{n-1}w$};
\node at (3.4, 8) {$(wz)^n w$};
\node at (-1.4, 8) {$(wz)^{n-1}w$};

\end{tikzpicture}

\end{minipage}
\caption{The relations for 2-braids}
\label{fig:elementary-twists}
\end{figure}

Now note that assigning letters of meridians as in the local situation in Figure \ref{fig:local-picture-pretzel-link}, we in fact obtain a generating set of the link group $\pi(P(l_1, \dots, l_k))$.


\begin{figure}[ht]
\centering
\begin{tikzpicture}
\draw[ultra thick] (0, -1.5) -- (0, 0) -- (1, 0) -- (1, -1.5);
\draw[ultra thick] (2, -1.5) -- (2, 0) -- (3, 0) -- (3, -1.5);

\begin{knot}
\strand[thick] (0.25, 0) .. controls +(0, 0.2) and +(0.2, 0) .. (-1, 0.2);
\strand[thick] (0.75, 0) .. controls +(0, 0.2) and +(0, 0.2) .. (2.25, 0);
\strand[thick] (2.75, 0) .. controls +(0, 0.2) and +(0.2, 0) .. (4, 0.2);
\end{knot}

\node at (0, 0.4) {$x$};
\node at (1, 0.4) {$y$};
\node at (2, 0.4) {$z$};
\node at (3, 0.4) {$w$};

\node at (0.5, -0.75) {$a$};
\node at (2.5, -0.75) {$b$};
\end{tikzpicture}

\caption{A local picture}
\label{fig:local-picture-pretzel-link}
\end{figure}

Putting these 2-braids together as in Figure \ref{fig:local-picture-pretzel-link} we obtain the following relation in the knot group from the requirement that $y = z$ according as to whether $a$ and $b$ are positive or negative:

\begin{itemize}
\setlength\itemsep{0em}
\item If both $a$ and $b$ are positive, then we obtain $(xy)^{a-1}x = (yw)^by.$
\item If $a$ is positive and $b$ is negative, we obtain $(xy)^{a-1}x = (wy)^{-b+1}w$.
\item If $a$ is negative and $b$ is positive, we obtain $(yx)^{-a}y = (yw)^b y$.
\item If both $a$ and $b$ are negative, then we obtain $(yx)^{-a}y = (wy)^{-b+1}w$.
\end{itemize}

All these relations follow from the Coxeter relations $(xy)^{|a|} = (yw)^{|b|} = 1$. Assigning generators as in Figure \ref{fig:local-picture-pretzel-link} we get a quotient of the desired form.
\end{proof}

\begin{corollary}
Pretzel links satisfy the meridional rank conjecture.
\end{corollary}
%TODO cite

\begin{proof}
This is just Corollary \ref{cor:coxeter-links-meridional-rank}.
\end{proof}

It might be worth pointing out that the explicit Coxeter quotient obtained is described by the matrix

$$
\renewcommand\arraystretch{1.2}
M = \left( \begin{matrix}
1 & l_1 & \infty & \cdots & \cdots &\cdots & \infty & l_n \\
l_1 & 1 & l_2 & \infty & \cdots & \cdots & \infty & \infty \\
\infty & l_2 & 1 & l_3 & \infty &\cdots & \infty & \infty \\
\vdots & \infty  & l_3 & 1 & \ddots & \ddots & \vdots & \vdots \\
\vdots & \vdots & \infty & \ddots & \ddots & \ddots & \infty & \vdots \\
\vdots & \vdots & \vdots & \ddots &\ddots & 1 & \l_{n-2} & \infty \\
\infty & \infty & \infty & \cdots & \infty & l_{n-2} & 1 & l_{n-1} \\
l_n & \infty & \infty & \cdots & \cdots & \infty  & l_{n-1} & 1
\end{matrix} \right).$$

\newpage

\appendix
\section{Appendix}\label{sec:data}
Table \ref{tab:cox-quotients-10-crossings} consists of the Coxeter quotients we found for $3$-bridge knots of crossing number $10$. It was computed using the same algorithm as in Section \ref{subsec:list-of-quotients}. No quotients were found for $10_{79}, 10_{80}, 10_{81}, 
10_{83}$, $10_{86}$, $10_{88}$, $10_{89}$, $10_{91}$, $10_{92}$, $10_{94}$, $10_{95}$, $10_{96}$, $10_{97}$,
$10_{100}$, $10_{101}$, $10_{103}$, $10_{104}$, $10_{105}$, $10_{106}$, $10_{107}$, $10_{109}$, $10_{110}$, $10_{111}$, $10_{114}$, $10_{115}$, $10_{116}$, $10_{117}$, $10_{118}$, $10_{119}$, $10_{121}$, $10_{122}$, $10_{123}$,
$10_{148}$, $10_{149}$, $10_{150}$, $10_{151}$, $10_{152}$, $10_{153}$, $10_{154}$, $10_{155}$, $10_{156}$, $10_{158}$,
$10_{160}$, $10_{161}$, $10_{162}$ and $10_{163}$. The knots that are not mentioned are $2$-bridge knots.

\begin{table}[htb]
\newcommand{\correctspace}{$\;\;\,$}
\centering
\begin{minipage}[t]{0.5\textwidth}
\centering
\begin{tabular}[t]{c|c}
Knot & Coxeter Quotients \\
\hline
\verticalcenter{$10_{46}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{47}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{48}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{49}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{50}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{51}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{52}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{53}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{54}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{55}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{56}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{57}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{58}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\ 
\verticalcenter{$10_{59}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\ 
\verticalcenter{$10_{60}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\ 
\verticalcenter{$10_{61}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{62}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{63}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{64}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{65}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{66}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{67}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$5$}}} \\
\verticalcenter{$10_{68}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$5$}}} \\
\verticalcenter{$10_{69}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$5$}}} \\
\verticalcenter{$10_{70}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{71}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{72}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{73}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{76}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{77}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{78}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{82}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{84}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{85}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{87}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{90}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{93}$} & \verticalcenter{\coxathreetype{$5$}} \\
\end{tabular}
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\centering
\begin{tabular}[t]{c|c}
Knot & Coxeter Quotients \\
\hline
\verticalcenter{$10_{98}$}\rule{0pt}{4ex} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$\infty$}}} \\
\verticalcenter{$10_{99}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$\infty$}}} \\
\verticalcenter{$10_{102}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{108}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{112}$} & \verticalcenter{\coxathreetype{$5$}} \\\verticalcenter{$10_{113}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{120}$} & \verticalcenter{\coxtwothreethree} \\
\verticalcenter{$10_{124}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{125}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{126}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{127}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{128}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{129}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{130}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{131}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{132}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{133}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{134}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{135}$} & \verticalcenter{\coxathreetype{$7$}} \\
\verticalcenter{$10_{136}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\
\verticalcenter{$10_{137}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\
\verticalcenter{$10_{138}$} & \correctspace\verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxathreetypedouble{$5$}{$5$}}} \\
\verticalcenter{$10_{139}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{140}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{141}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{142}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{143}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{144}$} & \verticalcenter{\coxfourthreethree} \\
\verticalcenter{$10_{145}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{146}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$5$}}} \\\verticalcenter{$10_{147}$} & \verticalcenter{\verticalcenter{\coxathreetype{$5$}} and \verticalcenter{\coxthreethreethreetype{$5$}}} \\
\verticalcenter{$10_{157}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{159}$} & \verticalcenter{\coxathreetype{$5$}} \\
\verticalcenter{$10_{164}$} & \verticalcenter{\coxtwothreethree} \\ \verticalcenter{$10_{165}$} & \verticalcenter{\coxtwothreethree}
\end{tabular}
\end{minipage}
\caption{List of Coxeter knots with bridge index $3$ and crossing number $10$}
\label{tab:cox-quotients-10-crossings}
\end{table}


\newpage

\bibliography{biblio}
\bibliographystyle{plain}

\end{document}